### 2013-02-16 doc/icml2013/evaluation.tex
edit

We generated synthetic data using covariates $x$ sampled uniformly over the $b$-dimensional
unit hypercube $[-1,1]^b$ and considered non-linear featurizations of
this data that conformed to the identifiability criteria discussed in
\sectionref{sec:algo}. The coefficients $\{\beta_h\}$ were drawn from a standard Gaussian.

As an example, one set of features we considered in the uni-dimensional
setting were $\{1, x, x^4, x^7\}$. The data and the curves fit using
Spectral Experts, EM with random initializations and EM initialized with
the parameters recovered using spectral experts are shown in
\figureref{fig:curves}. We note that even on well separated data such as
this, EM converged to the global optima only 13\% of the time.

\begin{figure*}[t]
  \centering
  \subfigure[Spectral]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{A comparison between Spectral Experts and EM. The dashed lines
  on the left denote the solution recovered by Spectral Experts. Whilst
  not a perfect fit, it provides an good initialization for EM to find
  the true global minima. The dotted lines on the right show different
  local optima found by EM on this example.}
  \label{fig:curves}
\end{figure*}

@@

\tableref{tbl:parameter-recovery} presents the Fro\"ebenius norm of the
difference between true and estimated parameters for the model, averaged
over 20 different random instances for each feature set and 10 attempts
for each instance. The experiments were run using $N = 500,000$ samples.

>>>>

We generated synthetic data as follows:
First, we generated a vector $t$ sampled uniformly over the $b$-dimensional
unit hypercube $[-1,1]^b$.
Then, to get the actual covariates $x$, we applied a non-linear function of $t$
that conformed to the identifiability criteria discussed in
\sectionref{sec:algo}.
The coefficients $\{\beta_h\}$ were drawn from a standard Gaussian.

As an example, one feature map we considered in the one-dimensional
setting was $x = (1, t, t^4, t^7)$. The data and the curves fit using
Spectral Experts, EM with random initializations and EM initialized with
the parameters recovered using Spectral Experts are shown in
\figureref{fig:curves}. We note that even on well-separated data such as
this, EM converged to the correct basin of attraction only 13\% of the time.

\begin{figure*}[t]
  \centering
  \subfigure[Spectral]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{A comparison between Spectral Experts and EM. The dashed lines
  on the left denote the solution recovered by Spectral Experts. While
  not a perfect fit, it provides an good initialization for EM to find
  the true global minima. The dotted lines on the right show different
  local optima found by EM on this example.}
  \label{fig:curves}
\end{figure*}

@@

\tableref{tbl:parameter-recovery} presents the Frobenius norm of the
difference between true and estimated parameters for the model, averaged
over 20 different random instances for each feature set and 10 attempts
for each instance. The experiments were run using $N = 500,000$ samples.
